---
title: "`r params$title`"
subtitle: "`r params$subtitle`"
author: "Richard Blackwell"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: html_document
params:
  title: Referral-To-Treatment (RTT) Model
  subtitle: <strong>RK9</strong> - University Hospitals Plymouth<br><strong>110</strong> - Trauma and Orthopaedics
  obj_file: D:\RWorkspace\devon_rtt_model\output\RK9_C110\RK9_C110.RObj
  output_dir: D:\RWorkspace\devon_rtt_model\output\RK9_C110
  sel_bins: c(78:104)
  sel_bins_desc: 78 weeks and over
---

<hr></hr>

```{r setup, include=FALSE}
# Load libraries, declare functions, load data and add logo
library(tidyverse)
library(reshape2)
library(gganimate)
#library(plotly)

palRTTReport <- c('ribbon1' = 'lightskyblue', 'ribbon2' = 'dodgerblue2', 'ribbon3' = 'mediumblue', 'highlight1' = 'white')
# Ribbon plot
fnCreateRibbonPlot <- function(chart_data, title, x, y, caption = paste0('Sim Name:', sim_name)){
  # Covert the chart_data array into a data frame and add the period field
  plt <- ggplot(data = chart_data) %+%
    theme_bw(base_size = 12) %+%
    theme(plot.title = element_text(hjust = 0.5)) %+%
    labs(title = title, x = x, y = y, caption = caption) %+%
    geom_ribbon(aes(x = period, ymin = `0%`, ymax = `2.5%`), fill = palRTTReport['ribbon1']) %+%
    geom_ribbon(aes(x = period, ymin = `2.5%`, ymax = `25%`), fill = palRTTReport['ribbon2']) %+%
    geom_ribbon(aes(x = period, ymin = `25%`, ymax = `50%`), fill = palRTTReport['ribbon3']) %+%
    geom_line(aes(x = period, y = `50%`), color = palRTTReport['highlight1'], linewidth = 1) %+%
    geom_ribbon(aes(x = period, ymin = `50%`, ymax = `75%`), fill = palRTTReport['ribbon3']) %+%
    geom_ribbon(aes(x = period, ymin = `75%`, ymax = `97.5%`), fill = palRTTReport['ribbon2']) %+%
    geom_ribbon(aes(x = period, ymin = `97.5%`, ymax = `100%`), fill = palRTTReport['ribbon1'])
  return(plt)
}

# Create the selected bins vector
sel_bins <- eval(parse(text = params$sel_bins))+1

# Load the RObj data
load(file = params$obj_file)

# Add logo to the report
htmltools::img(src = knitr::image_uri('./img/swahsn.png'), 
               alt = 'logo', 
               style = 'position:absolute; top:-50px; right:0; padding:20px; width:300px; height:225px;')

```

## Waiting Lists

### Non-Admitted - Total Waiting List Size

```{r waiting_list_nonadm_total, echo=FALSE}
# Create the waiting list totals by period and trial and calculate the minimum, maximum, 2.5th, 25th, 75th and 97.5th centiles, and median values for plotting
df_chart_data <- as.data.frame(
  t(
    apply(
      apply(wl_nonadm[,,], c(1,3), sum), 
      1,
      quantile,
      probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1)))
  ) %>% 
  mutate(period = c(0:sim_periods), .before = 1)

title <- str_wrap('Forecast for Total Size of Non-Admitted RTT Waiting List', width = 120)
x <- 'Forecast Week'
y <- 'Number of Patients'
caption <- sprintf('Sim Params: [%s: Periods=%d, Bins=%d, Trials=%d]',
                   sim_name, sim_periods, sim_bins, sim_trials)
plt <- fnCreateRibbonPlot(df_chart_data, title, x, y, caption)
plt

start_wl <- df_chart_data$`50%`[df_chart_data$period == 0]
end_wl <- df_chart_data$`50%`[df_chart_data$period == sim_periods]
```

The non-admitted waiting list **`r ifelse(start_wl>end_wl,'decreased','increased')`** from **`r start_wl`** at period 0 to **`r end_wl`** at period `r sim_periods` with a 95% prediction at period `r sim_periods` of **`r round(df_chart_data[df_chart_data$period == sim_periods,3],1)` to `r round(df_chart_data[df_chart_data$period == sim_periods,7],1)`**.


### Admitted - Total Waiting List Size

```{r waiting_list_adm_total, echo=FALSE}
# Create the waiting list totals by period and trial and calculate the minimum, maximum, 2.5th, 25th, 75th and 97.5th centiles, and median values for plotting
df_chart_data <- as.data.frame(
  t(
    apply(
      apply(wl_adm[,,], c(1,3), sum), 
      1,
      quantile,
      probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1)))
  ) %>% 
  mutate(period = c(0:sim_periods), .before = 1)

title <- str_wrap('Forecast for Total Size of Admitted RTT Waiting List', width = 120)
x <- 'Forecast Week'
y <- 'Number of Patients'
caption <- sprintf('Sim Params: [%s: Periods=%d, Bins=%d, Trials=%d]',
                   sim_name, sim_periods, sim_bins, sim_trials)
plt <- fnCreateRibbonPlot(df_chart_data, title, x, y, caption)
plt

start_wl <- df_chart_data$`50%`[df_chart_data$period == 0]
end_wl <- df_chart_data$`50%`[df_chart_data$period == sim_periods]
```

The admitted waiting list **`r ifelse(start_wl>end_wl,'decreased','increased')`** from **`r start_wl`** at period 0 to **`r end_wl`** at period `r sim_periods` with a 95% prediction at period `r sim_periods` of **`r round(df_chart_data[df_chart_data$period == sim_periods,3],1)` to `r round(df_chart_data[df_chart_data$period == sim_periods,7],1)`**.

### Non-Admitted - Patients Waiting `r params$sel_bins_desc`

```{r waiting_list_nonadm_selected, echo=FALSE}
# Create the waiting list totals by period and trial and calculate the minimum, maximum, 2.5th, 25th, 75th and 97.5th centiles, and median values for plotting
df_chart_data <- as.data.frame(
  t(
    apply(
      apply(wl_nonadm[,sel_bins,], c(1,3), sum), 
      1,
      quantile,
      probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1)))
  ) %>% 
  mutate(period = c(0:sim_periods), .before = 1)

title <- str_wrap(paste0('Forecast for Non-Admitted RTT Waiting List for Patients Waiting ', params$sel_bins_desc), width = 120)
x <- 'Forecast Week'
y <- 'Number of Patients'
caption <- sprintf('Sim Params: [%s: Periods=%d, Bins=%d, Trials=%d]',
                   sim_name, sim_periods, sim_bins, sim_trials)
plt <- fnCreateRibbonPlot(df_chart_data, title, x, y, caption)
plt

start_wl <- df_chart_data$`50%`[df_chart_data$period == 0]
end_wl <- df_chart_data$`50%`[df_chart_data$period == sim_periods]
```

The non-admitted waiting list for patients waiting `r params$sel_bins_desc` **`r ifelse(start_wl>end_wl,'decreased','increased')`** from **`r start_wl`** at period 0 to **`r end_wl`** at period `r sim_periods` with a 95% prediction at period `r sim_periods` of **`r round(df_chart_data[df_chart_data$period == sim_periods,3],1)` to `r round(df_chart_data[df_chart_data$period == sim_periods,7],1)`**.


### Admitted - Total Waiting List Size

```{r waiting_list_adm_selected, echo=FALSE}
# Create the waiting list totals by period and trial and calculate the minimum, maximum, 2.5th, 25th, 75th and 97.5th centiles, and median values for plotting
df_chart_data <- as.data.frame(
  t(
    apply(
      apply(wl_adm[,sel_bins,], c(1,3), sum), 
      1,
      quantile,
      probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1)))
  ) %>% 
  mutate(period = c(0:sim_periods), .before = 1)

title <- str_wrap(paste0('Forecast for Admitted RTT Waiting List for Patients Waiting ', params$sel_bins_desc), width = 120)
x <- 'Forecast Week'
y <- 'Number of Patients'
caption <- sprintf('Sim Params: [%s: Periods=%d, Bins=%d, Trials=%d]',
                   sim_name, sim_periods, sim_bins, sim_trials)
plt <- fnCreateRibbonPlot(df_chart_data, title, x, y, caption)
plt

start_wl <- df_chart_data$`50%`[df_chart_data$period == 0]
end_wl <- df_chart_data$`50%`[df_chart_data$period == sim_periods]
```

The admitted waiting list for patients waiting `r params$sel_bins_desc` **`r ifelse(start_wl>end_wl,'decreased','increased')`** from **`r start_wl`** at period 0 to **`r end_wl`** at period `r sim_periods` with a 95% prediction at period `r sim_periods` of **`r round(df_chart_data[df_chart_data$period == sim_periods,3],1)` to `r round(df_chart_data[df_chart_data$period == sim_periods,7],1)`**.
