---
title: "`r params$title`"
subtitle: "`r params$subtitle`"
author: "Richard Blackwell"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: html_document
params:
  title: Referral-To-Treatment (RTT) Model
  subtitle: <strong>###</strong> - Someone's Trust<br><strong>###</strong> - Selected Specialty
---

<hr></hr>
```{r setup, echo = FALSE}
# Load libraries, declare functions and load data
library(tidyverse)
library(reshape2)
library(gganimate)
library(plotly)

# Load the RObj data
load(file = 'D:/Workspace/devon_rtt_model/output/RH8_C130/RH8_C130.RObj')

subset_list <- list('>=104 wks' = c(104),
                    '>=78 wks' = c(78:104),
                    '>=65 wks' = c(65:104),
                    '>=52 wks' = c(52:104),
                    '>=18 wks' = c(18:104),
                    '<18 wks' = c(1:17))

fnPlotConfidenceBands <- function(df, title_label, xaxis_label, yaxis_label){
  pal_bands <- c('Outer' = '#deebf7',
                 'Middle' = '#6baed6',
                 'Inner' = '#08519c',
                 'Median' = '#FFFFFF')
  
  plt <- ggplot(df) %+%
    theme_bw(base_size = 12) %+%
    theme(plot.title = element_text(hjust = 0.5)) %+%
    labs(title = str_wrap(title_label, width = 80), x = xaxis_label, y = yaxis_label) %+%
    geom_ribbon(aes(x = period, ymin = P0.000, ymax = P0.025, fill = 'Outer'), alpha = 0.6) %+%
    geom_ribbon(aes(x = period, ymin = P0.025, ymax = P0.250, fill = 'Middle'), alpha = 0.6) %+%
    geom_ribbon(aes(x = period, ymin = P0.250, ymax = P0.500, fill = 'Inner'), alpha = 0.6) %+%
    geom_ribbon(aes(x = period, ymin = P0.500, ymax = P0.500, fill = 'Median'), color = 'black', alpha = 0.6) %+%
    geom_ribbon(aes(x = period, ymin = P0.500, ymax = P0.750, fill = 'Inner'), alpha = 0.6) %+%
    geom_ribbon(aes(x = period, ymin = P0.750, ymax = P0.975, fill = 'Middle'), alpha = 0.6) %+%
    geom_ribbon(aes(x = period, ymin = P0.975, ymax = P1.000, fill = 'Outer'), alpha = 0.6) %+%
    geom_line(aes(x = period, y = P0.500), color = 'white', linewidth = 1, alpha = 1) %+%
    guides(fill = guide_legend(title = 'Interval', override.aes = list(alpha = 0.2))) %+%
    scale_fill_manual(breaks = c('Outer', 'Middle', 'Inner', 'Median'), values = pal_bands, labels = c('Outer' = 'Min. to Max.', 'Middle' = '25% to 75%', 'Inner' = '2.5% to 97.5%', 'Median' = 'Median'))
  plt
  
  return(plt)
}

fnPlotProfileAnimation <- function(df, title_label, xaxis_label, yaxis_label, fill_colour = '#08519c', prob_scale = FALSE){
  plt <- ggplot(data = df_plotdata) %+%
    theme_bw(base_size = 12) %+%
    theme(plot.title = element_text(hjust = 0.5)) %+%
    labs(title = str_wrap(title_label, width = 80), x = x_label, y = y_label) %+%
    geom_bar(aes(x = bin, y = value, group = period), stat = 'identity', fill = fill_colour)
    if(prob_scale)
      plt <- plt %+% scale_y_continuous(label = scales::percent)
    plt <- plt %+% transition_time(period)
  return(plt)
}
```

## 1. Capacity Volume

```{r capacity_volume, echo = FALSE, fig.width = 9}
# 1. Capacity Volume ----
# ***********************

# * 1.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(t(apply(cap_vol_adm[,], MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Admitted Capacity Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 1.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(t(apply(cap_vol_nonadm[,], MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Non-Admitted Capacity Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 2. Non-RTT Volume

```{r nonrtt_volume, echo = FALSE, fig.width = 9}
# 2. Non-RTT Volume ----
# **********************

# * 2.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(t(apply(nonrtt_vol_adm[,], MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Admitted Non-RTT Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 2.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(t(apply(nonrtt_vol_nonadm[,], MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Non-Admitted Non-RTT Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 3. Clock Stop Volume

```{r clockstop_volume, echo = FALSE, fig.width = 9}
# 3. Clock Stop Volume ----
# *************************

# * 3.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(t(apply(cap_vol_adm - nonrtt_vol_adm, MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Admitted Clock Stop Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 3.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(t(apply(cap_vol_nonadm - nonrtt_vol_nonadm, MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Non-Admitted Clock Stop Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)
```

# 4. Clock Stop Profile (Unweighted) ----

```{r clockstop_profile, echo = FALSE}
# 4. Clock Stop Profile (Unweighted) ----
# ***************************************

# * 4.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(apply(cs_adm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Admitted Clock Stops by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean Clock Stops (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 4.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(apply(cs_nonadm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Non-Admitted Clock Stops by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean Clock Stops (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 5. Clock Stop Profile (Probability)

```{r clockstop_profile_prob, echo = FALSE}
# 5. Clock Stop Profile (Probability) ----
# ****************************************

# * 5.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(apply(cs_adm, c(1,2), mean)/apply(wl_adm[1:52,,], c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

df_plotdata <- df_plotdata %>%
  left_join(
    df_plotdata %>% 
      group_by(period) %>%
      summarise(total = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'period'
  ) %>%
  mutate(value = value/total) %>%
  replace_na(list(value = 0))

title_label <- 'Admitted Clock Stop Probability by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Clock Stop Probability'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label, prob_scale = TRUE)

# * 5.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(apply(cs_nonadm, c(1,2), mean)/apply(wl_nonadm[1:52,,], c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

df_plotdata <- df_plotdata %>%
  left_join(
    df_plotdata %>% 
      group_by(period) %>%
      summarise(total = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'period'
  ) %>%
  mutate(value = value/total) %>%
  replace_na(list(value = 0))

title_label <- 'Non-Admitted Clock Stop Probability by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Clock Stop Probability'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label, prob_scale = TRUE)
```

## 6. Demand Volume
```{r demand_volume, echo = FALSE, fig.width = 9}
# 6. Demand Volume ----
# *********************

# * 6.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(t(apply(dem_vol_adm, MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Admitted Demand Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 6.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(t(apply(dem_vol_nonadm, MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Non-Admitted Demand Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 7. Demand Profile (Unweighted)

```{r demand_profile, echo = FALSE}
# 7. Demand Profile (Unweighted) ----
# ***********************************

# * 7.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(apply(dem_adm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Admitted Clock Starts by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean Clock Starts (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 7.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(apply(dem_nonadm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Non-Admitted Clock Starts by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean Clock Starts (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 8. Demand Profile (Probability)
```{r demand_profile_prob, echo = FALSE, include = FALSE}
# 8. QUERY REMOVE? Demand Profile (Probability) ----
# **************************************************

# * 8.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(apply(dem_adm, c(1,2), mean)/apply(wl_adm[1:52,,], c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

df_plotdata <- df_plotdata %>%
  left_join(
    df_plotdata %>% 
      group_by(period) %>%
      summarise(total = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'period'
  ) %>%
  mutate(value = value/total) %>%
  replace_na(list(value = 0))

title_label <- 'Admitted Clock Start Probability by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Clock Start Probability'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label, prob_scale = TRUE)

# * 8.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(apply(dem_nonadm, c(1,2), mean)/apply(wl_nonadm[1:52,,], c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

df_plotdata <- df_plotdata %>%
  left_join(
    df_plotdata %>% 
      group_by(period) %>%
      summarise(total = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'period'
  ) %>%
  mutate(value = value/total) %>%
  replace_na(list(value = 0))

title_label <- 'Non-Admitted Clock Start Probability by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Clock Start Probability'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label, prob_scale = TRUE)
```

# 9. Conversion Volume

```{r conversion_volume, echo = FALSE, fig.width = 9}
# 9. Conversion Volume ----
# *************************

# * 9.1. Admitted ----
# ````````````````````
df_plotdata <- data.frame(t(apply(conv_vol_adm, MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Admitted to Non-Admitted Conversion Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 9.2. Non-admitted ----
# ````````````````````````
df_plotdata <- data.frame(t(apply(conv_vol_nonadm, MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Non-Admitted to Admitted Conversion Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 10. Conversion Profile (Unweighted)

```{r conversion_profile, echo = FALSE}
# 10. Conversion Profile (Unweighted) ----
# ****************************************

# * 10.1. Admitted ----
# `````````````````````
df_plotdata <- data.frame(apply(conv_adm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Admitted to Non-Admitted Conversions by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean Conversions (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 10.2. Non-admitted ----
# `````````````````````````
df_plotdata <- data.frame(apply(conv_nonadm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Non-Admitted to Admitted Conversions by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean Conversions (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 11. Conversion Profile (Probability)

```{r conversion_profile_prob, echo = FALSE}
# 11. Conversion Profile (Probability) ----
# *****************************************

# * 11.1. Admitted ----
# `````````````````````
df_plotdata <- data.frame(apply(conv_adm, c(1,2), mean)/apply(wl_adm[1:52,,], c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

df_plotdata <- df_plotdata %>%
  left_join(
    df_plotdata %>% 
      group_by(period) %>%
      summarise(total = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'period'
  ) %>%
  mutate(value = value/total) %>%
  replace_na(list(value = 0))

title_label <- 'Admitted to Non-Admitted Conversion Probability by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Conversion Probability'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label, prob_scale = TRUE)

# * 11.2. Non-admitted ----
# `````````````````````````
df_plotdata <- data.frame(apply(conv_nonadm, c(1,2), mean)/apply(wl_nonadm[1:52,,], c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

df_plotdata <- df_plotdata %>%
  left_join(
    df_plotdata %>% 
      group_by(period) %>%
      summarise(total = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'period'
  ) %>%
  mutate(value = value/total) %>%
  replace_na(list(value = 0))

title_label <- 'Non-Admitted to Admitted Conversion Probability by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Conversion Probability'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label, prob_scale = TRUE)
```

## 12. ROTT Volume
```{r rott_volume, echo = FALSE, fig.width = 9}
# 12. ROTT Volume ----
# *******************

# * 12.1. Admitted ----
# `````````````````````
df_plotdata <- data.frame(t(apply(rott_vol_adm, MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Admitted ROTT Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 12.2. Non-admitted ----
# `````````````````````````
df_plotdata <- data.frame(t(apply(rott_vol_nonadm, MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
  rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
  mutate(period = as.integer(rownames(.)), .before = 1)

title_label <- 'Non-Admitted ROTT Volume with Simulation Intervals'
xaxis_label <- 'Period'
yaxis_label <- 'Volume'

fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 13. ROTT Profile (Unweighted)

```{r rott_profile, echo = FALSE}
# 13. ROTT Profile (Unweighted) ----
# **********************************

# * 13.1. Admitted ----
# `````````````````````
df_plotdata <- data.frame(apply(rott_adm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Admitted Removals Other Than Treatment (ROTT) by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean ROTT (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 13.2. Non-admitted ----
# `````````````````````````
df_plotdata <- data.frame(apply(rott_nonadm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Non-Admitted Removals Other Than Treatment (ROTT) by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean ROTT (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 14. ROTT Profile (Probability)

```{r rott_profile_prob, echo = FALSE}
# 14. ROTT Profile (Probability) ----
# ***********************************

# * 14.1. Admitted ----
# `````````````````````
df_plotdata <- data.frame(apply(rott_adm, c(1,2), mean)/apply(wl_adm[1:52,,], c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

df_plotdata <- df_plotdata %>%
  left_join(
    df_plotdata %>% 
      group_by(period) %>%
      summarise(total = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'period'
  ) %>%
  mutate(value = value/total) %>%
  replace_na(list(value = 0))

title_label <- 'Admitted Removals Other Than Treatment (ROTT) Probability by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'ROTT Probability'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label, prob_scale = TRUE)

# * 14.2. Non-admitted ----
# `````````````````````````
df_plotdata <- data.frame(apply(rott_nonadm, c(1,2), mean)/apply(wl_nonadm[1:52,,], c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 1:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

df_plotdata <- df_plotdata %>%
  left_join(
    df_plotdata %>% 
      group_by(period) %>%
      summarise(total = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'period'
  ) %>%
  mutate(value = value/total) %>%
  replace_na(list(value = 0))

title_label <- 'Non-Admitted Removals Other Than Treatment (ROTT) Probability by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'ROTT Probability'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label, prob_scale = TRUE)
```

## 15. Waiting List Profile

```{r waiting_list_profile, echo = FALSE}
# 15. Waiting List Profile ----
# *****************************

# * 15.1. Admitted ----
# `````````````````````
df_plotdata <- data.frame(apply(wl_adm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 0:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Admitted Waiting List by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean Waiting List (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)

# * 15.2. Non-admitted ----
# `````````````````````````
df_plotdata <- data.frame(apply(wl_nonadm, c(1,2), mean)) %>% 
  rename_with(.fn = ~as.character(c(0:sim_bins))) %>%
  mutate(period = 0:sim_periods, .before = 1) %>%
  pivot_longer(cols = 2:NCOL(.), names_to = 'bin', values_to = 'value') %>%
  mutate(bin = as.integer(bin))

title_label <- 'Mean Non-Admitted Waiting List by Wait Bin and Period: {frame_time}'
x_label <- 'Weeks Waited'
y_label <- 'Mean Waiting List (over simulations)'

fnPlotProfileAnimation(df_plotdata, title_label, xaxis_label, yaxis_label)
```

## 16. Waiting List Subsets

```{r waiting_list_subsets, echo = FALSE, fig.width = 9}
# 16. Waiting List Subsets ----
# *****************************

# * 16.1. Admitted ----
# `````````````````````

plots_adm <- list()
tables_adm <- data.frame()
for(ni in c(1:length(subset_list))){
  # Check to see if length of subset is only one waiting list bin and adjust MARGIN of apply accordingly
  if(length(subset_list[[ni]])==1){
    # Only two dimensions resulting filtering (period, trial)
    margin = c(1,2)
  } else {
    # Three dimensions resulting filtering (period, bin, trial) and apply will applied to period and trial
    margin = c(1,3)
  }
  
  df_plotdata <- data.frame(t(apply(apply(wl_adm[, unname(subset_list[[ni]]), ], margin, sum), MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
    rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
    mutate(period = as.integer(rownames(.)), .before = 1)
  
  title_label <- paste0('Admitted Waiting List Volume Waiting ', names(subset_list[ni]), ' with Simulation Intervals')
  xaxis_label <- 'Period'
  yaxis_label <- 'Patients'
  
  plots_adm[[ni]] <- fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)
  tables_adm <- tables_adm %>% bind_rows(df_plotdata %>% mutate(subset = names(subset_list[ni])))
}

for(p in plots_adm){
  show(p)
}

# * 16.2. Non-Admitted ----
# `````````````````````````

plots_nonadm <- list()
tables_nonadm <- data.frame()
for(ni in c(1:length(subset_list))){
  # Check to see if length of subset is only one waiting list bin and adjust MARGIN of apply accordingly
  if(length(subset_list[[ni]])==1){
    # Only two dimensions resulting filtering (period, trial)
    margin = c(1,2)
  } else {
    # Three dimensions resulting filtering (period, bin, trial) and apply will applied to period and trial
    margin = c(1,3)
  }
  
  df_plotdata <- data.frame(t(apply(apply(wl_nonadm[, unname(subset_list[[ni]]), ], margin, sum), MARGIN = c(1), quantile, probs = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1.0)))) %>%
    rename_with(.fn = ~c('P0.000', 'P0.025', 'P0.250', 'P0.500', 'P0.750', 'P0.975', 'P1.000')) %>%
    mutate(period = as.integer(rownames(.)), .before = 1)
  
  title_label <- paste0('Non-Admitted Waiting List Volume Waiting ', names(subset_list[ni]), ' with Simulation Intervals')
  xaxis_label <- 'Period'
  yaxis_label <- 'Patients'
  
  plots_nonadm[[ni]] <- fnPlotConfidenceBands(df_plotdata, title_label, xaxis_label, yaxis_label)
  tables_nonadm <- tables_nonadm %>% bind_rows(df_plotdata %>% mutate(subset = names(subset_list[ni])))
}

for(p in plots_nonadm){
  show(p)
}
```
